---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!--You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>. -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Genetic Interaction Network IdentifieR (GINIR)

<!-- badges: start -->
<!-- badges: end -->

GINIR leverages data generated by the [Cancer Dependency Map (DepMap) project](https://depmap.org/portal/) to identify cancer cell lines with mutations of interest and performs in-silico genetic interaction screens. A manuscript describing the process is being prepared.

Current DepMap data used is version 20Q1 and was downloaded through the DepMap data portal. The data was distributed and used under the terms and conditions of [CC Attribution 4.0 license](https://creativecommons.org/licenses/by/4.0/). 
 

<!-- Below this line are default template stuff that will be updated as the package comes together -->

## Installation

You can install the released version of GINIR from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("GINIR")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ytakemon/GINIR")
```
## Examples (coming soon)

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(GINIR)
## basic example code
```

## Session Info 
```{r sessioninfo}
sessionInfo()
```